--

title: "EDA"

author: "mohsin"

date: "27 November 2016"

output:

  html_document: default

  pdf_document: default

---

```{r, include=FALSE}

library(dplyr)

library(ggplot2)

```

```{r}

train_data <- read.csv("~/Learning/Data/kaggle/house_prices/train.csv")

str(train_data)

calc_corr <- function(var_data){

  indices <- sapply(var_data, function(x) !is.na(x))

  clean_data <- var_data[indices]

  prices <- train_data$SalePrice[indices]

  cor(clean_data, prices)

}

hist_category <- function(var_data) {

  ggplot(data.frame(var_data), aes(x=var_data)) + geom_bar()

}

summary_category <- function(var_data){

  cat(paste0("levels : ", levels(var_data), "\n"))

  hist_category(var_data)

  ggplot(train_data, aes(x=var_data, y=SalePrice)) + geom_boxplot()

}

plot_price_vs_var <- function(var_data){

  ggplot(train_data, aes(x = var_data, y=SalePrice)) +geom_point()

}

summary_cont <- function(var_data){

  cat("summary is ")

  cat(summary(var_data))

  boxplot(var_data)

  # Correlation with the price

  cat("Correlation with the sale price is ",calc_corr(var_data))

}

```

## Univariate analysis

1) ID -lite

### 2) MSSubClass : The building class

```{r}

factor_mssubclass_levels <- as.factor(train_data$MSSubClass)

levels(factor_mssubclass_levels)

ggp <- ggplot(data.frame(factor_mssubclass_levels) , aes(x=factor_mssubclass_levels))

ggp + geom_bar()

ggplot(train_data, aes(x=factor_mssubclass_levels, y=SalePrice)) + geom_boxplot()

```

The data is not uniformly distributed

3) MSZoning : The general zoning classification

```{r}

levels(train_data$MSZoning)

ggplot(data.frame(train_data$MSZoning), aes(x=train_data$MSZoning)) + geom_bar()

ggplot(train_data, aes(x=MSZoning, y=SalePrice)) + geom_boxplot()

```

### 3) Lot Frontage

```{r}

summary(train_data$LotFrontage)

boxplot(train_data$LotFrontage)

ggplot(train_data, aes(x = LotFrontage, y=SalePrice)) +geom_point()

# Correlation with the price

calc_corr(train_data$LotFrontage)

```

### 4) Lot area : Linear feet of street connected to property

```{r, include=FALSE}

summary(train_data$LotArea)

ggplot(train_data, aes(x = LotArea, y=SalePrice)) +geom_point()

boxplot(train_data$LotArea)

# Correlation with the price

calc_corr(train_data$LotArea)

```

```{r}

plot_price_vs_var(train_data$LotArea)

summary_cont(train_data$LotArea)

```

### 5) Street : Type of road access

```{r}

hist_category(train_data$Street)

summary_category(train_data$Street)

```

I think that the above varibale can be removed as no entropy is there in the data

### 6) Alley: Type of alley access

```{r}

var_data <- train_data$Alley

hist_category(var_data)

summary_category(var_data)

```

Again not required as we have lot of NAs

### 7) LotShape: General shape of property

```{r}

var_data <- train_data$LotShape

hist_category(var_data)

summary_category(var_data)

```

### 8) LandContour: Flatness of the property

```{r}

var_data <- train_data$LandContour

hist_category(var_data)

summary_category(var_data)

```

### 9) Utilities: Type of utilities available

```{r}

var_data <- train_data$Utilities

hist_category(var_data)

summary_category(var_data)

```

This can also be removed as no entropy in the data

### 10) LotConfig: Lot configuration

```{r}

var_data <- train_data$LotConfig

hist_category(var_data)

summary_category(var_data)

```

This can also be removed as no entropy in the data

### 11) LandSlope: Slope of property

```{r}

var_data <- train_data$LandSlope

hist_category(var_data)

summary_category(var_data)

```

This can also be removed as no entropy in the data

### 12) Neighborhood: Physical locations within Ames city limits

```{r}

var_data <- train_data$Neighborhood

hist_category(var_data)

summary_category(var_data)

```
